Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-06 paper/post_tci.tex
Tuning hyper-parameters rewritten

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
The three hyper-parameters, $\lambda_1$, $\lambda_2$ and $k$
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are 
not known in advance, and thus not considered for the purpose of this
tuning. Thus, we compare our reconstruction with the best possible baseline TV reconstruction by choosing the $\lambda_1$ that gives the best SSIM for TV reconstruction. Further, this value was retained for our spatially-varying
prior-based reconstruction as well, that is, the value optimized for
the TV-only regularizer is maintained for the method proposed in this
paper.  In principle, one could have jointly optimized both
$\lambda_1$ and $\lambda_2$ to get even better results compared to the
one we have in Sections~\ref{sec:results_with_imaging_model},
and~\ref{sec:results_without_imaging_model}.

The value of $\lambda_2$
largely depends on the amount of artefacts one aims to remove by the
use of object-prior at the cost of their dominance in the new
regions. This value is chosen omnisciently, i.e., with the chosen $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM. This  was found to lie between $(0,3)$ for
our datasets. In practice however, one may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.

The hyper-parameter $k$ defines the sensitivity of the weights map to

>>>>

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
The aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction when optimal hyperparameter values for $\lambda_1$, $\lambda_2$ and $k$ are chosen.  In this regard, we assume the ground-truth to be known. Specifically, $\lambda_1$ was tuned to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are 
not known in advance, and thus not considered for the purpose of this
tuning. This optimal $\lambda_1$ was retained for spatially-varying prior-based reconstruction. With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth. %The value of $\lambda_2$ influences the amount of artefacts that can be removed by the use of object-prior at the expense of its dominance in new regions. %This value was found to lie between $(0,3)$ for our datasets.
%In principle, one could have jointly optimized both $\lambda_1$ and $\lambda_2$ to get even better results compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}. 
In practice however, since ground-truth will never be available, these parameters must be tuned using only the set of templates available.  One of the templates can be assumed to be a pseudo-test, and a grid search can be performed to get the best possible hyperparameter values. These values can then be used for reconstructing the `real' test volume.

%in the nvone may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.

$k$ defines the sensitivity of the weights map to
